Glasgow Hackerspace CIC Articles of Association

### 2024-03-20 articles.tex
Remove schedule parts from TOC

\setcounter{section}{0}
\setcounter{subsection}{0}

@@

\subsection*{Defined terms}
\subsection{\mdseries\normalsize{In the Articles, unless the context requires otherwise, the following terms shall have the following meanings:}}

@@

\subsection{\mdseries\normalsize{Subject to clause 3 of this Schedule, any reference in the Articles to an enactment includes a reference to that enactment as re-enacted or amended from time to time and to any subordinate legislation made under it.}}
\subsection{\mdseries\normalsize{Unless the context otherwise requires, other words or expressions contained in these Articles bear the same meaning as in the Companies Act 2006 as in force on the date when the Articles become binding on the Company.}}

>>>>

\setcounter{section}{0}
\setcounter{subsection}{0}
\setcounter{subsubsection}{0}

@@

\subsection*{Defined terms}
\subsubsection*{In the Articles, unless the context requires otherwise, the following terms shall have the following meanings:}

@@

\subsubsection*{Subject to clause 3 of this Schedule, any reference in the Articles to an enactment includes a reference to that enactment as re-enacted or amended from time to time and to any subordinate legislation made under it.}
\subsubsection*{Unless the context otherwise requires, other words or expressions contained in these Articles bear the same meaning as in the Companies Act 2006 as in force on the date when the Articles become binding on the Company.}
